---
title: "glm data analysis"
author: "Lina"
date: "December 15, 2018"
output: word_document
---
#Part I: market segment by kmean 
##kmean elbow selected clusters
###cluster 4

```{r}
library(dplyr)
new <- subset(dfkep, cluster == 4)
model1 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict1 <- predict(model1, new, se.fit=T,interval="confidence", level=.95)
new1 <- cbind(predict1$fit,new)
plot(model1)
summary(model1)
newp <- new1 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp$sales)
sum(newp$sales)
```


###cluster 2

```{r}
library(dplyr)
new <- subset(dfkep, cluster == 2)
model2 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict2 <- predict(model2, new, se.fit=T,interval="confidence", level=.95)
new2 <- cbind(predict2$fit,new)
plot(model2)
summary(model2)
newp2 <- new2 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp2, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp2$sales)
sum(newp2$sales)
```

###cluster6
```{r}
library(dplyr)
new <- subset(dfkep, cluster == 6)
model3 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict3 <- predict(model3, new, se.fit=T,interval="confidence", level=.95)
new3 <- cbind(predict3$fit,new)
plot(model3)
summary(model3)
newp3 <- new3 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp3, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```


```{r}
summary(newp3$sales)
sum(newp3$sales)
```

##market segment by kmean silhouette selected clusters
###cluster4
```{r}
new <- subset(dfksp, cluster == 4)
model4 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict4 <- predict(model4, new, se.fit=T,interval="confidence", level=.95)
new4 <- cbind(predict4$fit,new)
plot(model4)
summary(model4)
newp4 <- new4 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp4, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```


```{r}
summary(newp4$sales)
sum(newp4$sales)
```

###cluster5

```{r}
new <- subset(dfksp, cluster == 5)
model5 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict5 <- predict(model5, new, se.fit=T,interval="confidence", level=.95)
new5 <- cbind(predict5$fit,new)
plot(model5)
summary(model5)
newp5 <- new5 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp5, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp5$sales)
sum(newp5$sales)
```

###cluster1
```{r}
new <- subset(dfksp, cluster == 1)
model6 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict6 <- predict(model6, new, se.fit=T,interval="confidence", level=.95)
new6 <- cbind(predict6$fit,new)
plot(model6)
summary(model6)
newp6 <- new6 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
```

##market segment by kmean gap selected clusters
###cluster 5

```{r}
new <- subset(dfkgp, cluster == 5)
model7 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict7 <- predict(model7, new, se.fit=T,interval="confidence", level=.95)
new7 <- cbind(predict7$fit,new)
plot(model7)
summary(model7)
newp7 <- new7 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp7, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```
```{r}
summary(newp7$sales)
sum(newp7$sales)
```

###cluster6
```{r}
new <- subset(dfkgp, cluster == 6)
model8 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict8 <- predict(model8, new, se.fit=T,interval="confidence", level=.95)
new8 <- cbind(predict8$fit,new)
plot(model8)
summary(model8)
newp8 <- new8 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp8, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp8$sales)
sum(newp8$sales)
```

###cluster1
```{r}
new <- subset(dfkgp, cluster == 1)
model9 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict9 <- predict(model9, new, se.fit=T,interval="confidence", level=.95)
new9 <- cbind(predict9$fit,new)
plot(model9)
summary(model9)
newp9 <- new9 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp9, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```
```{r}
summary(newp9$sales)
sum(newp9$sales)
```

###cluster 4
```{r}
new <- subset(dfkgp, cluster == 4)
model10 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict10 <- predict(model10, new, se.fit=T,interval="confidence", level=.95)
new10 <- cbind(predict10$fit,new)
plot(model10)
summary(model10)
newp10 <- new10 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp10, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp10$sales)
sum(newp10$sales)
```



#part II: hierarchical analysis
##elbow selected clusters (cluster2,3,4)
###cluster 2

```{r}
new <- subset(hccutep, cluster == 2)
model11 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict11 <- predict(model11, new, se.fit=T,interval="confidence", level=.95)
new11 <- cbind(predict11$fit,new)
plot(model11)
summary(model11)
newp11 <- new11 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp11, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp11$sales)
sum(newp11$sales)
```


###cluster 3

```{r}
new <- subset(hccutep, cluster == 3)
model12 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict12 <- predict(model12, new, se.fit=T,interval="confidence", level=.95)
new12 <- cbind(predict12$fit,new)
plot(model12)
summary(model12)
newp12 <- new12 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp12, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp12$sales)
sum(newp12$sales)
```

###cluster 4

```{r}
new <- subset(hccutep, cluster == 4)
model13 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict13 <- predict(model13, new, se.fit=T,interval="confidence", level=.95)
new13 <- cbind(predict13$fit,new)
plot(model13)
summary(model13)
newp13 <- new13 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp13, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```


```{r}
summary(newp13$sales)
sum(newp13$sales)
```

##si selected clusters (cluster2,3,4)
###cluster 2

```{r}
new <- subset(hccutsp, cluster == 2)
model14 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict14 <- predict(model14, new, se.fit=T,interval="confidence", level=.95)
new14 <- cbind(predict14$fit,new)
plot(model14)
summary(model14)
newp14 <- new14 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp14, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

###cluster 3

```{r}
new <- subset(hccutsp, cluster == 3)
model15 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict15 <- predict(model15, new, se.fit=T,interval="confidence", level=.95)
new15 <- cbind(predict15$fit,new)
plot(model15)
summary(model15)
newp15 <- new15 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp15, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp15$sales)
sum(newp15$sales)
```

###cluster 4
```{r}
new <- subset(hccutsp, cluster == 4)
model16 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict16 <- predict(model16, new, se.fit=T,interval="confidence", level=.95)
new16 <- cbind(predict16$fit,new)
plot(model16)
summary(model16)
newp16 <- new16 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp16, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
```

```{r}
summary(newp16$sales)
sum(newp16$sales)
```
##hcgap
###cluster 4
```{r}
new <- subset(hccutpp, cluster == 4)
model17 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict17 <- predict(model17, new, se.fit=T,interval="confidence", level=.95)
new17 <- cbind(predict17$fit,new)
plot(model17)
summary(model17)
newp17 <- new17 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp17, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
summary(newp17$sales)
sum(newp17$sales)
```

###cluster5
```{r}
new <- subset(hccutpp, cluster == 5)
model18 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict18 <- predict(model18, new, se.fit=T,interval="confidence", level=.95)
new18 <- cbind(predict18$fit,new)
plot(model18)
summary(model18)
newp18 <- new18 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp18, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
summary(newp18$sales)
sum(newp18$sales)
```

###cluster8
```{r}
new <- subset(hccutpp, cluster == 22)
model19 <- lm(salesl~PC1+PC2+PC3+PC4, data = new)
predict19 <- predict(model19, new, se.fit=T,interval="confidence", level=.95)
new19 <- cbind(predict19$fit,new)
plot(model19)
summary(model19)
newp19 <- new19 %>% subset(salesl == 0) %>% mutate(sales=exp(fit)-1, up=exp(upr)-1, low=exp(lwr)-1)
ggplot(newp19, aes(PC4,sales))+ geom_point(aes(y=sales), color="red") +geom_line(aes(y=low), color = "orange") + geom_line(aes(y=up), color = "green")
summary(newp19$sales)
sum(newp19$sales)
```

#part III: pam
##elbow selected clusters (cluster2,3,4)
###cluster 2